Toward Resolved Simulations of Burning Fronts in Thermonuclear X-ray Bursts

### 2018-09-29 astronum_2018/astronum-xrb.tex
typo
Merge Yuri's edits

Figure~\ref{fig:xrb} shows the flame structure for an initial 2D run
at 0.007~s.  The burning layer is only about 10~m high.  Underneath is
\isot{Ni}{56}, representative of the underlying neutron star, and
above it is very a low density ($10^{-4}~\gcc$) buffer.  Only a
portion of the vertical extent is shown.  The top panel shows the
temperature structure.  The initial perturbation reached to $2\times
10^4~\mathrm{cm}$, so at this point, the extent of the burnt region
has nearly doubled.  The flame structure is quite wide, since there
are multiple burning stages beyond just helium to carbon, and this
shows up in the composition.  This is seen more clearly in the next
panel which shows the mean molecular weight of the nuclei ($\bar{A}$).
We see that the further behind the head of the flame we are, the heavier
the ash nuclei.  We also see where the head of the flame
appears lifted off of the base of the burning layer---unburned
material underlies the spreading flame.  This appears
reminiscent of the flame structure seen in the earlier simulations of
\cite{cavecchi:2012}. \MarginPar{Yuri, would you agree?} The third panel shows the energy generation rate.
It is strongest just above the neutron star surface, behind the flame.
We again see that the head of the flame is detached from the base
of the atmosphere, with the strongest burning at the head of the flame
slightly higher up in the atmosphere.   Finally, the bottom
panel shows the velocity through the plane of the simulation---this is
induced by the Coriolis force as the burning front spreads laterally.
A tight hurricane structure has setup as a result of the flame
spreading.  This is the geostrophic balance discussed in
\cite{SPIT_ETAL02}.    These calculations are ongoing and will be
the subject of a detailed study in the near future.

>>>>

Figure~\ref{fig:xrb} shows the flame structure for an initial 2D run
at 0.007~s.  The burning layer is only about 10~m high.  Underneath is
\isot{Ni}{56}, representative of the underlying neutron star, and
above it is a very low density ($10^{-4}~\gcc$) buffer.  Only a
portion of the vertical extent is shown.  The top panel shows the
temperature structure.  The initial perturbation reached to $2\times
10^4~\mathrm{cm}$, so at this point, the extent of the burnt region
has nearly doubled.  The flame structure is quite wide, since there
are multiple burning stages beyond just helium to carbon, and this
shows up in the composition.  This is seen more clearly in the next
panel which shows the mean molecular weight of the nuclei ($\bar{A}$).
We see that the further behind the head of the flame we are, the heavier
the ash nuclei.  We also see the head of the flame
appears lifted off of the base of the burning layer---unburned
material underlies the spreading flame.  This is
reminiscent of the flame structure seen in the earlier simulations of
\cite{cavecchi:2012}.  The third panel shows the energy generation rate.
It is strongest just above the neutron star surface, behind the flame.
We again see that the head of the flame is detached from the base
of the atmosphere, with the strongest burning at the head of the flame
slightly higher up in the atmosphere.   Finally, the bottom
panel shows the velocity through the plane of the simulation---this is
induced by the Coriolis force as the burning fluid expands and begins to spreads laterally.
A tight hurricane structure has setup as a result of the flame
spreading.  This is the geostrophic balance discussed in
\cite{SPIT_ETAL02}.    These calculations are ongoing and will be
the subject of a detailed study in the near future.
